Scikit-learn: machine learning without learning the machinery

### 2014-05-18 article.tex
typo

\paragraph{Project vision}
%
Scikit-learn was born from the observation that most standard
machine-learning algorithms were out of reach of the users that could
most benefit from them: researchers --biologists, climate
scientists, experimental physicists-- or developers --for web
services or domain-specific applications.
%
Implementations mostly consisted of scattered piece of code to download
on researchers' web pages, with the notable exception
statistic-specific environments such as the R language \cite{Rmanual}, or
the Weka java library \cite{hall2009weka}.

>>>>

\paragraph{Project vision}
%
Scikit-learn was born from the observation that most standard
machine-learning algorithms were out of reach of the users that could
most benefit from them: researchers --biologists, climate
scientists, experimental physicists-- or developers --for web
services or domain-specific applications.
%
Implementations mostly consisted of scattered piece of code to download
on researchers' web pages, with the notable exception of
statistic-specific environments such as the R language \cite{Rmanual}, or
the Weka java library \cite{hall2009weka}.
